Painting with Triangles

### 2014-06-06 paper.tex
Answered the two questions and changed render to process

A set of contours define the outline of a stroke. For simply connected strokes, those without holes, 
one contour describes the whole stroke. However, strokes with holes, such as a circle or 
figure-eight, will have more than one contour.
Converting a user's mouse motion into a set of contours requires two steps.
First, the user's mouse movements are captured by a set of polygons which can be
rendered to yield a rasterized version of the stroke. \modified{This rasterization happens at the resolution of the current window. Therefore
whatever the artist sees on the screen is the basis for the vectorization.}
Second, to obtain the contours the stroke is rasterized in black and marching squares~\cite{lorensen1987}
is used to extract iso-contours of 50\% gray. This returns a very dense set of points,
which we reduce through a pruning process to
get a sparse but accurate representation of the contour.
The pruning procedure walks around the contour to form an approximating polygon $P$,
greedily eliding vertices whenever they lie within a small threshold distance of $P$. \modified{We use
a threshold of 0.5 pixels at the current zoom level, which works well empirically.}

@@

\subsection{Complexity}
To find the growth rates of the algorithm we performed two experiments. 
First, the program drew fifty random strokes without zooming.
Next, the program drew fifty random strokes with random zoom level for each stroke.
Geometry grows fastest when many strokes are composited on one another. When not zooming, strokes
must cover the same area of canvas over and over. This
results in more geometry and therefore takes longer to render. The zooming case explores different
areas of the canvas and therefore results in less overlapping geometry. This situation should result
in less complex geometry and therefore take less time.

@@

Figure~\ref{fig:timing} gives a similar result for the cumulative time strokes take to render. Both
the zooming and non-zooming cases grow non-linearly over time. However, the non-zooming case takes
longer for the reasons described. \modified{For example, the first ten strokes in both cases take about 2 seconds
to render, while the last ten strokes take about 20 seconds in the non-zooming case and 7 seconds in the zooming case.}
It is not unexpected that even the zooming case grows non-linearly
since even though the geometries involved are not becoming very complicated, the geometry of the entire
canvas is increasing linearly and must be considered even if the entire canvas is not re-triangulated.

@@

\subsection{Performance}
Performance is measured on a 1.8 GHz Core i5 MacBook Air with 8GB of RAM and an Intel
HD 4000 graphics card.  The current implementation uses Python and PyOpenGL. Python's performance is slower than
a lower level implementation in C++ would be. The preview rasterization of a new stroke on 
the canvas is interactive with
no lag. However, the actual process to take a stroke from rasterization to triangle
representation on the canvas can be slow. On a blank canvas, strokes take less than
one second to process. However, on a canvas with lots of geometry a stroke that overlaps
that geometry can take several seconds to render. Some of this could be alleviated by a carefully optimized implementation. However, there are many calculations
necessary for the old points affected by the new stroke and the points associated with the
new stroke itself. Since these geometries can become arbitrarily complicated (in pathological cases), these
calculations can take arbitrarily long.
% This brings us to the final point, simplification.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % \includegraphics[width=\columnwidth]{graphs/numtriangles}
    \includegraphics[height=1.2in]{graphs/numtriangles}
    \caption{Number of triangles}
    \label{fig:numtriangles}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % \includegraphics[width=\columnwidth]{graphs/cumulativetime}
    \includegraphics[height=1.2in]{graphs/cumulativetime}
    \caption{Rendering time}
    \label{fig:timing}
  \end{subfigure}%
  \caption{For paintings of 50 random strokes, the left graph shows the number of triangles in the canvas as of stroke $x$, and the right graph shows the cumulative render time of the painting. The blue points are the non-zooming case, while the red points are the zooming case.}
\end{figure}

>>>>

A set of contours define the outline of a stroke. For simply connected strokes, those without holes, 
one contour describes the whole stroke. However, strokes with holes, such as a circle or 
figure-eight, will have more than one contour.
Converting a user's mouse motion into a set of contours requires two steps.
First, the user's mouse movements are captured by a set of polygons which can be
rendered to yield a rasterized version of the stroke. \modified{This rasterization happens at the resolution of the current window, 1280x960. Therefore
whatever the artist sees on the screen is the basis for the vectorization.}
Second, to obtain the contours the stroke is rasterized in black and marching squares~\cite{lorensen1987}
is used to extract iso-contours of 50\% gray. This returns a very dense set of points,
which we reduce through a pruning process to
get a sparse but accurate representation of the contour.
The pruning procedure walks around the contour to form an approximating polygon $P$,
greedily eliding vertices whenever they lie within a small threshold distance of $P$. \modified{We use
a threshold of 0.5 pixels at the current zoom level, which works well empirically.}

@@

\subsection{Complexity}
To find the growth rates of the algorithm we performed two experiments. 
First, the program drew fifty random strokes without zooming.
Next, the program drew fifty random strokes with random zoom level for each stroke.
Geometry grows fastest when many strokes are composited on one another. When not zooming, strokes
must cover the same area of canvas over and over. This
results in more geometry and therefore takes longer to \modified{process this new stroke}. The zooming case explores different
areas of the canvas and therefore results in less overlapping geometry. This situation should result
in less complex geometry and therefore take less time.

@@

Figure~\ref{fig:timing} gives a similar result for the cumulative time strokes take to process \modified{after mouse up}. Both
the zooming and non-zooming cases grow non-linearly over time. However, the non-zooming case takes
longer for the reasons described. \modified{For example, the first ten strokes in both cases take about 2 seconds each
to process, while the last ten strokes take about 20 seconds each in the non-zooming case and 7 seconds each in the zooming case.}
It is not unexpected that even the zooming case grows non-linearly
since even though the geometries involved are not becoming very complicated, the geometry of the entire
canvas is increasing linearly and must be considered even if the entire canvas is not re-triangulated.

@@

\subsection{Performance}
Performance is measured on a 1.8 GHz Core i5 MacBook Air with 8GB of RAM and an Intel
HD 4000 graphics card.  The current implementation uses Python and PyOpenGL. Python's performance is slower than
a lower level implementation in C++ would be. The preview rasterization of a new stroke on 
the canvas is interactive with
no lag. However, the actual process to take a stroke from rasterization to triangle
representation on the canvas can be slow. On a blank canvas, strokes take less than
one second to process. However, on a canvas with lots of geometry a stroke that overlaps
that geometry can take several seconds to process. Some of this could be alleviated by a carefully optimized implementation. However, there are many calculations
necessary for the old points affected by the new stroke and the points associated with the
new stroke itself. Since these geometries can become arbitrarily complicated (in pathological cases), these
calculations can take arbitrarily long.
% This brings us to the final point, simplification.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % \includegraphics[width=\columnwidth]{graphs/numtriangles}
    \includegraphics[height=1.2in]{graphs/numtriangles}
    \caption{Number of triangles}
    \label{fig:numtriangles}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % \includegraphics[width=\columnwidth]{graphs/cumulativetime}
    \includegraphics[height=1.2in]{graphs/cumulativetime}
    \caption{Processing time}
    \label{fig:timing}
  \end{subfigure}%
  \caption{For paintings of 50 random strokes, the left graph shows the number of triangles in the canvas as of stroke $x$, and the right graph shows the cumulative process time of the painting. The blue points are the non-zooming case, while the red points are the zooming case.}
\end{figure}
